---
title: "Titanic data set with logistic Regression"
output: html_notebook
---

Read the data from secondary Storage
```{r}
#get the working dir.
getwd()
#read CSV trainig data
train <- read.csv("/home/ashok/Desktop/titanic/train .csv")
head(train)
#summary of training data-set
summary(train)
```
Training data set Information:-

Obeservations =891 
Features =12

Age has NA(missing) values.

```{r}
test <- read.csv("/home/ashok/Desktop/titanic/test .csv")
PassengerId=test$PassengerId
head(test)
summary(test)
```
Testing data set Information:-

Obeservations =418 
Features =12

Fare and Age has NA(missing) values.

Treatment for missing values

```{r}
hist(train$Age)
train$Age[is.na(train$Age)] = 29.07
test$Age[is.na(test$Age)] = 29.07
test$Fare[is.na(test$Fare)] = 35.627
```

```{r}
summary(train)
summary(test)
```


```{r}
train$Sex = ifelse(train$Sex=="female", 1, 0)
test$Sex = ifelse(test$Sex=="female", 1, 0)
```
```{r}
train$embarked_c = ifelse(train$Embarked=="C", 1, 0)
test$embarked_c = ifelse(test$Embarked=="C", 1, 0)

train$embarked_s = ifelse(train$Embarked=="S", 1, 0)
test$embarked_s = ifelse(test$Embarked=="S", 1, 0)
```

Select features from test and train data set
```{r}
head(train)
train = train[-c(1, 4, 9,11,12)]
head(test)
test = test[-c(3, 8,10,11)]
```

Detect and remove the outliers from Age column using boxplot 
```{r}

boxplot(train$Age)
train$Age = ifelse(train$Age>=52, 52, train$Age)
train$Age = ifelse(train$Age<=4, 4, train$Age)
test$Age = ifelse(test$Age>=52, 52, test$Age)
test$Age = ifelse(test$Age<=4, 4, test$Age)
boxplot(test$Age)
```
Detect and remove the outliers from Fare column using boxplot 

```{r}
boxplot(train$Fare)
train$Fare = ifelse(train$Fare>=136, 136, train$Fare)
test$Fare = ifelse(test$Fare>=136, 136, test$Fare)
```
Linear Regression model

```{r}
#import the "car" package
library(car)
#buliding the linear regression model
model <- lm(Survived~., data=train)
```

Logistic Regression model

```{r}
#Calculate the variance-infection for linear regression model
t = vif(model)
sort(t, decreasing=TRUE)

#buliding the model using logistic regression
model1<- glm(as.factor(Survived)~., family="binomial", data=train)

#summery of model
summary(model1)
```
Prediction

```{r}
# prediction
test$score <- predict(model1, newdata = test, type="response")
head(test$score)

#Using the threshold value is 0.56
test$Survived <- ifelse(test$score>=0.56, 1, 0)
head(test)
df=test[c(1,11)]
head(df)

#Write into CSV file
write.csv(df,file = "df.csv",row.names = FALSE)

```
